---
title: "Case Study"
author: Tanya Butt
output: html_document
  
---

```{r}
library(tidyverse)
library(leaflet)
library(p8105.datasets)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Load a dataset

```{r}
data("nyc_airbnb")
force(nyc_airbnb)
```

*How many rentals are there? Of what type? In what places?
*Is price correlated with review score?
*Which neighborhood is most popular? Most expensive?
*Which neighborhood has the highest reviews?
*Is availability related to price?
*Is room type related to neighborhood?
*Is length of stay related to neighborhood group (borough)?

```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(borough = neighbourhood_group)
```

Let's try to count things:

```{r}
nyc_airbnb %>% 
  janitor::tabyl(borough, room_type)

nyc_airbnb %>% 
  count(borough, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```

Let's look at price and room type.
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point() +
  facet_grid(. ~ room_type)
```

Price and Neighborhood

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
arrange(mean_price)

nyc_airbnb %>% 
  filter(borough == "Manhattan", price <= 1000) %>% 
  mutate(neighbourhood =
           fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() + 
  coord_flip() +
  facet_grid(. ~ room_type) 
```

Price versus location

```{r}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(5000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

## retry leaflet
```{r}
pal = colorNumeric("viridis", NULL)

nyc_airbnb %>% 
  mutate(
    labels = str_c("<b>", price, "</b><br>", stars)
  )

nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  mutate(
    labels = str_c("<b>Price", price, "</b><br>Stars:", stars)) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, 
                  color = ~pal(price))
```

